Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-22 paper.tex

\begin{keywords}
Containers; Security; Docker; Singularity; Neuroimaging.
\end{keywords}

@@

Containers, which provide operating system (OS) level virtualization, are very
popular. This is because they are very lightweight, flexible, resource-efficient,
provide fast development cycles, continuous delivery,
and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
is not supported by High Performance
Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
for HPC environments. It is used in many clusters including Compute Canada.
According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.

@@

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. Security
of containers is still most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Except web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping focus on HPC environments. This popularity of containers lead us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}.

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

\textit{RQ2:} Can we get rid of these vulnerabilities by updating the
images?

\textit{RQ3:} Can we get rid of these vulnerabilities by shrinking the
size of the image?

\textit{RQ4:} Can we get rid of these vulnerabilities by both updating
and shrinking image size?

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that, containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also Singularity came up with Stools, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in next section, we provide description
of materials and methods which summarizes our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. Next section of this paper is about the results. Here, we
present number of vulnerabilites that are present in the container images
which are used for data analysis on shared HPC clusters. Following section is about 
discussion of these results where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
rules that can be followed to secure container images for use in clusters.

@@

Container tools are capable of packing and running an application in an isolated environment that have
the application's dependencies,
required libraries and configuration files for the
application to function properly.

@@

Docker uses a client-server architecture, where client, containers, communicate to
the server, Docker Daemon, which is also known as Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

@@

As Docker is not suitable for HPC systems therefore, Singularity came up with a new approach
of packing and running applications in containers. 
In contrast to Docker,
Singularity does not run containers as root. Consequently, users cannot escalate
privileges in Singularity containers making it suitable for HPC environments.

@@

We used 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
we could not get 3 images and 2 images were already included in BIDS images.
Therefore we are left with a total 18 Boutiques images which include 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.
\end{comment}
So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
Table~\ref{sing} lists 6 Singularity images taken from Boutiques framework.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

\begin{figure}[H]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

@@

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

Ubuntu maintains its vulnerability database in Ubuntu launchpad or Ubuntu CVE tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
The status can be any one of the following:

@@

\textbf{pending:} The package (inside the given release) is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The package version that contains the fix is also
		  alongwith the status.

@@

\textbf{released-esm:} The package (inside the given release) was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by
		+esmN or /~esmN, indicating that this package version is available
		only via ESM.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\subsection{Image size Reduction process}
If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

@@

Our final experiment involves combination of both update and size reduction process
to lessen the number of vulnerabilities.
So in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same two scripts that
we used for earlier experiments.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
Figure~\ref{sing}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

@@

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
It was interesting to investigate the reasons of these differences.
%these scanners report different numbers and types of vulnerabilities.
%How their logic differs and what exactly is making these results different than each other.

@@

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example, CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}

@@

As the effect of update,
scanning results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
%\begin{comment}
%There are only two
%options, either you accept those vulnerabilities and use that image, or you discard that image.
%So one thing is clear here that even if we keep our images up to date there will be still some
%vulnerabilities that we have to face.
%\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images. 
%In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
In fact, this image combines original results of Figure~\ref{fig:graph1} with the results of update.
Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
significant number. Furthermore, a mild slope of vulnerabilities after the update shows that
there is a set of packages that contain vulnerabilities and have no fix yet. Also, these
vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
critical vulnerability are patched with high priority.
Besides that, it is also interesting to note that some images in the Figure~\ref{fig:graph2}
do not have update results. This is because some Linux distributions reached end-of-life and
are not getting updates anymore.

@@

\begin{figure}[H]
        \fbox{{\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/graphwithdeletedpackages.pdf}}}
	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
\end{figure}

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because reduction process takes a
while. We selected these five images at random. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief.
At first, we thought that we will have notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
the Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) number
of unnecessary packages that we deleted and \rom{2}) type of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this can be illustrated by Figure~\ref{deleted}.
Also, if we delete packages that contain a lot of vulnerabilites, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in the Figure~\ref{fig:bargraph}
shows no effect of size reduction alongwith update. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can reply upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
the pipeline to get Reprozip trace that can take upto several hours. Also, user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
branch of the program. So there should be some kind of coverage measurement.

>>>>

\begin{keywords}
Containers; Vulnerabilities; Docker; Singularity; Neuroimaging.
\end{keywords}

@@

Containers, which provide an operating system (OS) level virtualization, are
popular. This is because they are lightweight, flexible, resource-efficient,
provide fast development cycles, continuous delivery,
and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
is not supported by High Performance
Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
for HPC environments. It is used in many clusters including Compute Canada.
According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.

@@

However, two features of the Linux kernel,\textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Besides web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. This popularity of containers leads us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}.

To answer that question, we scan images that are used on Compute
Canada clusters by the Neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: Static scanning and Dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unauthorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

\textit{RQ2:} Can these vulnerabilities be reduced by updating the images?

\textit{RQ3:} Can these vulnerabilities be reduced by shrinking the size of the images?

\textit{RQ4:} What is the effect of both updating
and shrinking image size on vulnerabilities?

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that, containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also Singularity came up with Stools, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. The next section of this paper is about the results. Here, we
present a number of vulnerabilities that are present in the container images
which are used for data analysis on shared HPC clusters. Following section is about 
the discussion of these results where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
rules that can be followed to secure container images for use in clusters.

@@

Container tools are capable of packing and running an application in an isolated environment that has
the application's dependencies,
required libraries, and configuration files for the
application to function properly.

@@

Docker uses a client-server architecture, where client, containers, communicate to
the server, Docker Daemon, which is also known as the Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

@@

As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
of packing and running applications in containers. 
In contrast to Docker,
Singularity does not run containers as root. Consequently, users cannot escalate
privileges in Singularity containers making it suitable for HPC environments.

@@

We used 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
we could not get 3 images and 2 images were already included in BIDS images.
Therefore we are left with a total of 18 Boutiques images which include 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.
\end{comment}
So we have a total of 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
Table~\ref{sing} lists 6 Singularity images taken from the Boutiques framework.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

\begin{figure}
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
\end{figure}

@@

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

Ubuntu maintains its vulnerability database in the Ubuntu Launchpad or the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
The status can be any one of the following:

@@

\textbf{pending:} The package (inside the given release) is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The package version that contains the fix is also
		  along with the status.

@@

\textbf{released-esm:} The package (inside the given release) was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by
		+esmN or \char`\~esm, indicating that this package version is available
		only via ESM.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

@@

Our final experiment involves a combination of both update and size reduction process
to lessen the number of vulnerabilities.
So in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same two scripts that
we used for earlier experiments.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after the update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
Similarly, Figure~\ref{sing} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure*}[t]
	{\includegraphics[scale=1.5,width=\textwidth]
	{Figures/vulngraph.pdf}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure*}

\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
It was interesting to investigate the reasons for these differences.
%these scanners report different numbers and types of vulnerabilities.
%How their logic differs and what exactly is making these results different than each other.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}
\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

@@

\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example, CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database at that time. Due to which it is missed by Clair Scanner.

@@

@@

As the effect of update,
scanning results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
%\begin{comment}
%There are only two
%options, either you accept those vulnerabilities and use that image, or you discard that image.
%So one thing is clear here that even if we keep our images up to date there will be still some
%vulnerabilities that we have to face.
%\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images. 
%In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
In fact, this image combines the original results of Figure~\ref{fig:graph1} with the results of the update
experiment.
Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
significant number. Furthermore, a mild slope of vulnerabilities after the update shows that
there is a set of packages that contain vulnerabilities and have no fix yet. Also, these
vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
critical vulnerabilities are patched with high priority.
Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
do not have update results. This is because some Linux distributions reached end-of-life and
are not getting updates anymore.

@@

\begin{figure*}
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/graphwithdeletedpackages.pdf}}
	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
\end{figure*}

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because the reduction process takes a
while. We selected these five images at random. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted}.
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
branch of the program. So there should be some kind of coverage measurement.
